Figure: the scatterblob

### 2022-04-12 R/scatterblob.Rmd
modifying difficulty (and collaborativeness) for citeable code

Use even notation across text and figure

space out middle blobs
labels to x and y axis
homogenizing titles of ways to use github

@@

```{r}
library(readr)
scatterblob_data <- readr::read_csv("scatterblob_data.csv")
library(googlesheets4)
scatterblob_data <- googlesheets4::read_sheet(ss = "https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit?pli=1#gid=0")

@@

```{r}
names(scatterblob_data)
scatterblob_data$x1 <- scatterblob_data$`Degree of immediate collaborativeness X1`
scatterblob_data$x2 <- scatterblob_data$`Degree of immediate collaborativeness X2`
scatterblob_data$y <- scatterblob_data$`Cognitive load absolute`

my_data <- scatterblob_data[,c("Ways to use GitHub","y", "x1", "x2")]
my_data
```

@@

```{r}
my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
###############################################################
# start the pdf connection and set graphical parameters
###############################################################
pdf(file = "scatterblob_0.pdf", 
    width = 8.25, 
    height = 6, 
    bg = "transparent")
par(xpd = NA, 
    mai = c(1.02, 1, 0.82, 4), 
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5), 
     y = c(1.75, 9.75), 
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02) 
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(1, rep(1.05, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nmembers", 
                "Other \nlabs", 
                "The \ncommunity", 
                "The \npublic"))
text(x = c(1, 3, 5),
     y = 0.5, 
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(2, 4, 6, 8, 10), 
     cex = 0.7,
     adj = 1,
     labels = c("Elementary", 
                "Low \nintermediate", 
                "Intermediate", 
                "Pre- \nAdvanced", 
                "Very \nAdvanced"))
###############################################################
# plot scatter blobs
###############################################################
for (i in seq(nrow(scatterblob_data))) {
  X0 <- scatterblob_data$x1[i]
  X1 <- scatterblob_data$x2[i]
  Y <- scatterblob_data$`Cognitive load`[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 13)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = scatterblob_data$`Cognitive load`, 
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```
![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.pdf)

@@

```{r}
my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
###############################################################
# start the pdf connection and set graphical parameters
###############################################################
pdf(file = "scatterblob_1.pdf", 
    width = 8.25, 
    height = 6, 
    bg = "transparent")
par(xpd = NA, 
    mai = c(1.02, 1, 0.82, 4), 
    bty="n")
plot(x = c(0.5, 5.5), 
     y = c(0.5, 14), 
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02) 
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(-0.65, rep(-0.7, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nmembers", 
                "Other \nlabs", 
                "The \ncommunity", 
                "The \npublic"))
text(x = c(1, 3, 5),
     y = -1.7, 
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(0, 2, 4, 6, 8, 10, 12, 14), 
     cex = 0.7,
     adj = 1,
     labels = c("Beginner",
                "Elementary", 
                "Low\nintermediate",
                "Pre-\nintermediate",
                "Intermediate", 
                "Upper\nintermediate",
                "Pre-\nAdvanced", 
                "Very\nAdvanced"))
###############################################################
# plot scatter blobs on sequential cognitive load
###############################################################
for (i in seq(nrow(scatterblob_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 23)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y, 
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```

>>>>

Use even notation across text and figure:
homogenizing titles of ways to use github

@@

```{r}
#library(readr)
#scatterblob_data <- readr::read_csv("scatterblob_data.csv")
library(googlesheets4)
scatterblob_data <- googlesheets4::read_sheet(ss = "https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit?pli=1#gid=0")

@@

```{r}
names(scatterblob_data)
scatterblob_data$x1 <- scatterblob_data$`Min degree of collaborativeness X1`
scatterblob_data$x2 <- scatterblob_data$`Max degree of collaborativeness X2`
scatterblob_data$y_real <- scatterblob_data$`Cognitive load - real`
scatterblob_data$y_seq <- scatterblob_data$`Cognitive load - sequential`

my_data <- scatterblob_data[,c("Ways to use GitHub","y_seq", "y_real", "x1", "x2")]
my_data
```

@@

```{r}
my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
###############################################################
# start the pdf/png connection and set graphical parameters
###############################################################
# plot_format <- "pdf"
# plot_format <- "svg"
plot_format <- "png"
if (plot_format == "pdf") {
  pdf(file = "scatterblob_0.pdf",
      width = 8.25,
      height = 6,
      bg = "transparent")  
}
if (plot_format == "svg") {
  svg(filename = "scatterblob_0.svg",
      width = 8.25,
      height = 6,
      bg = "transparent")  
}
if (plot_format == "png") {
  png(file = "scatterblob_0.png",
      width = 8.25,
      height = 6,
      units = "in",
      res = 100,
      bg = "transparent")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(1.75, 9.75),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(1, rep(1.05, 4)),
     cex = 0.7,
     labels = c("Personal",
                "Lab \nmembers",
                "Other \nlabs",
                "The \ncommunity",
                "The \npublic"))
text(x = c(1, 3, 5),
     y = 0.5,
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(2, 4, 6, 8, 10),
     cex = 0.7,
     adj = 1,
     labels = c("Elementary",
                "Low \nintermediate",
                "Intermediate",
                "Pre- \nAdvanced",
                "Very \nAdvanced"))
###############################################################
# plot scatter blobs
###############################################################
for (i in seq(nrow(scatterblob_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y_real[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 13)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y_real,
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```
![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.pdf)

@@

```{r}
my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
###############################################################
# start the pdf/png/svg connection and set graphical parameters
###############################################################
 plot_format <- "pdf"
# plot_format <- "svg"
# plot_format <- "png"
if (plot_format == "pdf") {
  pdf(file = "scatterblob_1.pdf",
      width = 8.25,
      height = 6,
      bg = "transparent")  
}
if (plot_format == "svg") {
  svg(filename = "scatterblob_1.svg",
      width = 8.25,
      height = 6,
      bg = "transparent")  
}
if (plot_format == "png") {
  png(file = "scatterblob_1.png",
      width = 8.25,
      height = 6,
      units = "in",
      res = 100,
      bg = "transparent")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(0.5, nrow(my_data)),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(-0.65, rep(-0.7, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nmembers", 
                "Other \nlabs", 
                "The \ncommunity", 
                "The \npublic"))
text(x = c(1, 3, 5),
     y = -1.7, 
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(0, 2, 4, 6, 8, 10, 12, 14, 15.5), 
     cex = 0.7,
     adj = 1,
     labels = c("Beginner",
                "Elementary", 
                "Low\nintermediate",
                "Pre-\nintermediate",
                "Intermediate", 
                "Upper\nintermediate",
                "Pre-\nAdvanced",
                "Advanced",
                "Very\nAdvanced"))
###############################################################
# plot scatter blobs on sequential cognitive load
###############################################################
for (i in seq(nrow(scatterblob_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y_seq[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 23)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y_seq,
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```
